### 2023-10-09 main.tex
fix 2

\textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, we for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. By varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Thus, the coefficient of the above formula can be written as

@@

Therefore, we can write 

@@

			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{x=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{y}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}

@@

\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$. Indeed, the empty species does not produce changes in the correlations between the non-empty species. 
\paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by 
   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=1}^{N-1}\beta_{a}e_{aN}\co
which action on the occupation variable of a site is 
  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\mu}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
Therefore, taking the tensor product over the chain we obtain 
  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
By projecting over a vector $\langle \bm{\tau}|$ we have 
\begin{equation}\label{goodTP-S2}
  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{i=1}^L\left[ \delta_{\tau_i,\mu_i}+\delta_{N,\mu_i}\beta_{\tau_i} (1-\delta_{\tau_i,N})\right]
For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, using equation \eqref{ResulsBasis} and observing that 
	\left(1+\sum_{j=y}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\mu_{y},N})\right)
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\dt
Introducing $c_{x}$ defined as 
	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}
\begin{equation}\label{coefficients-psiSec}
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{y}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.
We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that

>>>>

\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, we for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. By varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Thus, the coefficient of the above formula can be written as

@@

Therefore, we write 

@@

			\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\beta_{\tau_{x}}^{(1-c_{x})(1-\delta_{\tau_{x},N})}

@@

\textbf{Remark}: In equation \eqref{ABS} we observe that when $\tau_{x}=N$ we have just a contribution of a factor $1$ on the product over $x$. Indeed, the empty species does not produce changes in the correlations between the non-empty species. \\ \\
\textbf{Remark:} If we consider the case $N=2$ we have that, for an arbitrary configuration $\bm{\tau}$, we can identify $|\bm{\tau}|=\sum_{x=1}^{L}\delta_{\tau_{x},1}$ occupied sites and the remaining $L-|\bm{\tau}|$ empty. We denote by $(x_{i})_{i\in\{1,\ldots,|\bm{\tau}|\}}$ the coordinates of the occupied sites. We introduce $q\in\{0,\ldots,|\bm{\tau}|\}$ and we rewrite \eqref{ABS} as
We introduce $\ell_{1},\ldots,\ell_{q}\in\{1,\ldots,L\}$ such that $\ell_{1}<\ell_{2}<\cdots<\ell_{q}$, and such that $\ell_{i}\in\{1,\ldots,|\bm{\tau}|\}$ for all $i\in\{1,\ldots,q\}$. Therefore, we can label each occupied coordinate by $x_{\ell_{i}}$. It follows that we have
	\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\mathbbm{1}_{\{c_{1}+\cdots+c_{L}=q\}}\prod_{k=1}^{q}\left(L+2-x_{k}-\sum_{i=x_{k}}^{L}c_{i}\right)=\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-(q-k+1)\right)\dt
Observing that
	\frac{\Gamma(L+2-q)}{\Gamma(2+L)}=\prod_{k=1}^{q}\frac{1}{(2+L-k)}\co
	\Psi^{'}(\bm{\tau})=\sum_{q=0}^{|\bm{\tau}|}(\alpha-\beta)^{q}\beta^{L-q}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq |\bm{\tau}|}\prod_{k=1}^{q}\frac{\left(L+1-x_{\ell_{k}}-q+k\right)}{(2+L-k)}\dt

\paragraph{Proof of formula \eqref{ABS-vect}} Using \eqref{S2-Inverse} we have $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$, thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by 
\begin{equation}
   \mathcal{S}_{2}^{-1}=\mathbbm{1}+\sum_{a=1}^{N-1}\beta_{a}e_{aN}\co
\end{equation}
which action on the occupation variable of a site is 
\begin{equation}
  \mathcal{S}_{2}^{-1} |\mu\rangle= |\mu\rangle+\delta_{N,\mu}\sum_{a=1}^{N-1}\beta_a|a\rangle\dt
\end{equation} 
Therefore, taking the tensor product over the chain we obtain 
\begin{equation}
  \left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\left( |\mu_1\rangle+\delta_{N,\mu_1}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)\otimes\ldots\otimes \left( |\mu_L\rangle+\delta_{N,\mu_L}\sum_{a=1}^{N-1}\beta_a|a\rangle\right)
\end{equation} 
By projecting over a vector $\langle \bm{\tau}|$ we have 
\begin{equation}\label{goodTP-S2}
  \langle \bm{\tau}|\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L} |\bm{\mu}\rangle=\prod_{i=1}^L\left[ \delta_{\tau_i,\mu_i}+\delta_{N,\mu_i}\beta_{\tau_i} (1-\delta_{\tau_i,N})\right]
\end{equation} 
For a fixed configuration $\bm{\mu}=(\mu_{1},\ldots,\mu_{L})$, using equation \eqref{ResulsBasis} and observing that 
\begin{equation}
	\left(1+\sum_{j=y}^{L}\delta_{\mu_{j},N}\right) =\left(2+L-y-\sum_{j=y}^{L}(1-\delta_{\mu_{y},N})\right)
\end{equation}
we obtain 
\begin{equation}
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\mu_{x},N})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\mu_{j},N})\right)\right)^{1-\delta_{\mu_{x},N}}\dt
\end{equation}
Introducing $c_{x}$ defined as 
\begin{equation}
	c_{x}(\mu_{x})=(1-\delta_{\mu_{x},N}) \qquad \forall x\in \{1,\ldots L\}
\end{equation}
we obtain 
\begin{equation}\label{coefficients-psiSec}
	\Psi^{''}(\bm{\mu})=\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{x=1}^{L}\left(\lambda_{\mu_{y}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}
\end{equation}
where, for the sake of notation we left understood the dependence on $\mu_{x}$ of $c_{x}$.
\begin{comment}
We introduce the following notation
\begin{equation}\label{notation1}
    e_{ab}=e_{a}^{b}=\left(\delta_{ac}\delta_{bd}\right)_{c,d\in\{1,\ldots,N\}}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
and 
\begin{equation}\label{notation2}
    e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}=\left(\delta_{(a,b),(e,f)}\delta_{(c,d),(g,h)}\right)_{e,f,g,h\in \{1,\ldots,N\}}\qquad \forall a,b,c,d\in \{1,\ldots,N\}
    \end{equation}
    that can be generalized for $e_{\tau_{1},\ldots,\tau_{L}}^{q_{1},\ldots,q_{L}}$ with $\tau_{1},\ldots,\tau_{L},q_{1},\ldots,q_{L}\in \{1,\ldots,N\}$. With this notation we have that
